Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-06-25 WRITEUP/ms.tex
minor wording

\begin{figure*}
\centering
\includegraphics[trim=0 0 0 0, clip, width=1.05\textwidth]{\figpath/3by2_clumpProp_allss}
\caption{Same as \Fig{larsons_single}, except star symbols are showing MCCs identified across all evolutionary stages traced in our simulation, which are color-coded by the SFR of \flower in those stages (see colorbar). Left panels show MCCs identified using a low density threshold of $n_{\rm cut}$\eq0.53\,\cc and right panels show MCCs
identified using a high density threshold of $n_{\rm cut}$\eq18.96\,\cc.
The biggest MCCs identified at lowest density thresholds, occupying the top right corner of the top left panel, correspond to the molecular 
disk and arms of \flower, and are broken down into smaller MCCs at higher density thresholds (see top right panel).
\label{fig:alpha16-28}}
\end{figure*}

@@

If constant column density (Larson's third relation) is truly a fundamental properties of molecular clouds % or the roughly linear relationship between $\rho$ and $R$ of MCCs.
(i.e., if virialization is a universal property of molecular clouds with negligible surface pressure), 
one would expect a single point in the $\sigma_{\rm gas}^2/R$--$\Sigma$ relation at a given gas mass surface density $\Sigma$. 
The variation in $\sigma_{\rm gas}^2/R$ with $\Sigma$ seen here suggests that column density is not a fundamental properties of 
molecular clouds. Previous studies suggest that the observed mass-size relation of molecular clouds 
is solely a result of $\rho\propto M R^{-3}$ and may be an artifact of the limited range of 
column densities a specific molecular line tracer is sensitive to \citep[][]{Ballesteros02a, Ballesteros11a}.
%For instance, \citet{Ballesteros02a} show that the density
%of clouds ($\rho$) is independent of their size ($R$) when one properly extract these quantities in three-dimensional space instead of
%two-dimensional space; the latter is done in \obs.
%When they project the clouds into two-dimensional space and measure the densities and sizes of clouds for a given
%line tracer, they find $\rho \propto R^{-1}$, which is unsurprising since $N_H$ is just a constant.
%They therefore argue that the mass-size relation is simply a result of $\rho\propto M R^{-3}$
%observed in 2D-space at a fixed column density (cf. an actual physical relation of $M \propto R^{4/3}$ claimed in
%observational studies). % where $\rho$ would be proportional to $R^{-1/2}$
%% since $M$ would then scale as $R^{3}$ (ånd naturally display a linear relationship in $\log M - \log R$ plot).

@@

% Starburst
In the starburst phase, MCCs have velocity dispersion and sizes similar to those in the accreting phase; however, 
MCCs in the starburst phase span a wider range in gas surface density 
(bottom panels of \Fig{larsons_single}) and have lower virial parameters, even
for MCCs with masses $<$\,10$^7$\,\Msun (i.e., excluding the molecular disk of \flower identified).
That is, more MCCs in the starburst phase of \flower are more susceptible to collapse, as expected.
The gas surface density of MCCs in both accreting and starburst phases is higher than that in the solar neighborhood
of the Milky Way and the LMC, but comparable to those observed in starburst galaxies and the nearby 
ultra-luminous IR galaxies (ULIRGs) \citep{Boulares90a, Scoville91a, Weiss01a, Hughes10a, Leroy15a}.
% LMC: 0.01 g cm^-2
% M82: 0.1 g cm^-2
% Arp 220: 7-20 g cm^-2
%
% Due to a time delay between cloud collapse and \SF, we also compare the virial parameter of MCCs in the pre-starburst phase and post-starburst phase.
%\Fig{alphaEvol} shows that most MCCs in the pre-starburst phase have even lower virial parameter than in the starburst phase. On the other hand,
%the virial parameter of MCCs in the post-starburst phase is higher than in both the pre-starburst and the starburst phase.
%This is consistent with our physical intuition of gas instability leading to \SF.

@@

The sizes of MCCs are dependent on the choice of $n_{\rm cut}$ in the following ways.
As mentioned in \Sec{dist}, the most massive cloud identified at low H$_2$ gas density thresholds
corresponds to the molecular disk of \flower, which is broken down into multiple smaller MCCs at higher 
$n_{\rm cut}$\footnote{That said, there are fewer MCCs at highest $n_{\rm cut}$ than the lowest $n_{\rm cut}$ 
 since there are fewer cells in the simulations with correspondingly high H$_2$ gas densities.}.
Second, excluding such structure, some MCCs are further broken down into smaller MCCs at higher $n_{\rm cut}$ 
(see top panels of \Fig{larsons_single}). 
At the resolution limit of our simulation, most MCCs studied in this work have $R\simeq$\,100\,pc.
%
%For instance, the cluster of points found at the lowest density threshold, 
%occupying the top right corner of the linewidth-size relation in the top left panel of \Fig{alpha16-28}, 
%are broken down into smaller MCCs at the highest density threshold (see top right panel of the same figure\footnote{Note
%that while the biggest MCCs are broken into smaller MCCs at higher $n_{\rm cut}$, 
%MCCs identified at lower density in the outskirts of \flower
%typically do not reach the density thresholds as $n_{\rm cut}$ increases. Hence, there are fewer MCCs at the highest density threshold.}).
%%
%These MCCs are smaller in size, and thus, occupy the leftward in the top right panel.

@@

At the highest density cut, only the densest gas structures are identified. This automatically excludes the molecular disk and arms 
of \flower. The virial parameter of these MCCs indicates that most of them are unstable against collapse 
(see middle right panel of \Fig{alpha16-28}).

@@

In this section, we compare the observable quantities of MCCs obtained from the simulations (e.g., $\sigma_{\rm gas}$, $R$, $M_{\rm gas}$, $\Sigma_{\rm gas}$) with those of molecular gas structures from \obs at lower redshift.
%%
%We exclude the biggest MCC identified in each evolutionary stage, which correspond to the main disk of \flower (i.e., the top right cluster of points in the linewidth-size relation of \Fig{larsons_single} and the top left panel of \Fig{alpha16-28}).
The MCCs of \flower have dynamics largely similar to those observed in $z$\ssim2 spatially resolved studies of gas-rich star-forming galaxies, in terms of their velocity dispersions, sizes, and gas surface densities (\Fig{larsons_single}; see e.g., \citealt{Swinbank11a}), with sizes of the order of $R\simeq$\,100\,pc and velocity dispersions of $\sigma_{\rm gas}\simeq$\,20$-$80\,\kms.
%
Their velocity dispersions are also comparable to those observed in the inner Milky way and nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a, Leroy15a}), which lies along the locus of $\sigma_{\rm gas}\propto R^{0.56}$. Such high velocity dispersion of MCCs in \flower is dominated by non-thermal energy (\Fig{vv}) and results from the injection of kinetic energy from recent \SF as \flower is assembling its stellar mass (given the high Mach numbers of MCCs; \Sec{distribution}). In fact, by the accreting stage (see \Fig{SFH}a) at $z\simeq$\,7.2, \flower has assembled a stellar mass of $M_\star$\eq7.5\E{9}\,\Msun.

@@

% different evolutionary stages
In terms of the Larson's linewidth-size relation, we do not find any major quantitative differences in the MCC properties with respect to those observed in the nearby Universe between the accreting and starburst phase of \flower (see \Fig{larsons_single}), which are separated by $\simeq$300\,Myr. However, MCCs in the \SB phase have lower $\alpha_{\rm vir}$ compared to the accreting phase. This is expected for \SF to proceed.

@@

Close resemblance of the $Q_{\rm eff}$ and $Q_{\star}$ maps indicates that contributions from the stellar component play an important role in governing the stability of the MCCs against perturbations. This can be understood since stars in \flower dominates the central part of the galaxy in mass, so their gravitational potential provides a non-negligible contribution to the instability. Similarly, contribution from the thickness of the disk is important in \flower since its disk is warped and has a scale height-to-radius ratio of $h/r_{\rm gal}$\ssim150\,pc/1\,kpc\,$\simeq$\,0.15.

That is, some MCCs are found in regions of $Q_{\rm gas}$\ssim1, which is consistent with the expectation that they correspond to regions of high surface densities that are gravitationally unstable. Note, however, that when including the stabilizing effects due to the stellar potential of \flower and the thickness of its disk (via $\sigma_z$, i.e., $Q_{\rm eff}$; see Equation~\ref{eqn:q_eff}), some of these MCCs are consistent with $Q_{\rm eff} > 1$.
%
This demonstrates the importance of accounting for stellar contribution and disk thickness when examining the stability of molecular gas structures. This consideration is especially relevant for the relatively evolved and enriched systems at high redshift, that are preferentially being imaged at high resolution with ALMA. In the outer regions of \flower, on the other hand, $Q_{\rm eff}$ resembles $Q_{\rm gas}$, with both $\log{Q_{\rm gas}}$ and $\log{Q_{\rm eff}} < -1$. Notably, these are the more gas-rich regions (see \Fig{sigma}).

The large virial parameters seen in some MCCs of \flower can be understood by first noting that fragmentation {\em can} happen in regions of low $Q$ (if we only consider instability against axisymmetric perturbations), but further evolution/collapse depends on the dynamics or equation of state of the gas.
%
Such fragmentation is expected to take place at the critical scale length $\lambda_{\rm crit} < 2 \pi^2 G \Sigma / \kappa^2$. Second, this fragmentation scale is greater than the typical size of GMCs.
%
This could be interpreted as a result of instability setting the scales for fragmentation, {\em but the truly star-forming regions correspond to the collapsing, denser, and cooler molecular structures that are on smaller scales}.
%
Thus, the high virial parameter found for some MCCs in \flower indicates that they are not the collapsing structures and are found in regions of $Q_{\rm eff}>1$. On the other hand, MCCs in (the denser) regions with a lower Toomre $Q_{\rm eff}$ parameter are unstable and \SF is expected to take place within its star-forming {\it clumps} and {\it cores} on smaller scales, where energy quickly dissipates.

If most of the MCCs in \flower are stable against collapse, how does it sustain its high SFR of $\sim$70\,\Msun\,yr\pmOne in the starburst phase? Such tension in the interpretation is understood as follows.
%
First, due to energy dissipation on small-scales, such MCCs are no longer supported by turbulence. This in turn enables sub-regions of the MCCs to collapse and potentially form OB associations out of these unbound MCCs \citep{Clark04a, Clark05a}.
% Mechanisms causing non-axisymmetric perturbations (e.g., arms) to the gravitational potential \MM{Gravitational instability is that mechanism (see e.g.\ Wada et al.'s classic review of the subject (2011, doi:10.1017/S1743921311000640), so this isn't really a separate mechanism.} can induce orbit crossing, shocks and dissipation in gas, promoting turbulence dissipation and collapse on smaller scales to trigger \SF. These mechanisms are likely important given high $Q_{\rm eff}$ found across \flower and its few tens of solar masses per year SFR, albeit sporadic.
Further, the SFR of \flower is very bursty and high SFR stages are only transient.
%
Finally, our results are limited by the resolution of the simulation, i.e., in \flower~we do not resolve \SF in {\it cores} and {\it clumps} as in the classical molecular cloud hierarchy. This re-iterates the statement about low $Q$ above.

@@

The sizes of MCCs are dependent on the choice of $n_{\rm cut}$, and thus, some of the MCCs within the main disk break into multiple MCCs at higher $n_{\rm cut}$. The $\sim$200\,pc-scale MCCs found with a low density threshold correspond to the arms of the disk of \flower and break down into smaller $\lesssim$100\,pc-scale MCCs at higher density thresholds.
%
Excluding the biggest MCC, the typical mass of MCCs is $10^{6.5}$\,\Msun. Similarly massive molecular structures have been observed in nearby star-forming and starburst galaxies \citep[e.g.,][]{Keto05a, DonovanMeyer13a, Colombo14a, Leroy15a}, and reported in idealized (no stellar feedback) isolated (no cosmological initial conditions) galaxy simulations done at higher resolution (e.g., $l_{\rm cell}\simeq3$\,pc in the 48\,kpc box studied by \citealt{Behrendt16a}). That said, the similar mass range found in MCCs of \flower\ is reassuring --- our results are not far off despite the resolution limit ($l_{\rm cell}\simeq$\,30\,pc). On the other hand, the gas velocity dispersion $\sigma_{\rm gas}$ is rather insensitive to the adopted density threshold.

>>>>

\begin{figure*}
\centering
\includegraphics[trim=0 0 0 0, clip, width=1.05\textwidth]{\figpath/3by2_clumpProp_allss}
\caption{Same as \Fig{larsons_single}, except star symbols are showing molecular gas structures identified across all evolutionary stages traced in our simulation, which are color-coded by the SFR of \flower in those stages (see colorbar on the right). Left panels show structures identified using a low density threshold of $n_{\rm cut}$\eq0.53\,\cc and the right panels show those identified using a high density threshold of $n_{\rm cut}$\eq18.96\,\cc.
The biggest MCCs identified at lowest density thresholds, occupying the top right corner of the top left panel, correspond to the molecular 
disk and arms of \flower, and are broken down into smaller MCCs at higher density thresholds (see top right panel). 
Notably less MCCs in the right panels owing to the fact that only few MCCs with neighboring cells reaching high H$_2$ densities of $n_{\rm cut}\simeq$19\,\cc.
The high velocity dispersion in \flower is largely driven by non-thermal pressure (see \Fig{vv}).
\label{fig:alpha16-28}}
\end{figure*}

@@

If constant column density (Larson's third relation) is truly a fundamental properties of molecular clouds % or the roughly linear relationship between $\rho$ and $R$ of MCCs.
(i.e., if virialization is a universal property of molecular clouds with negligible surface pressure), 
one would expect a single point in the $\sigma_{\rm gas}^2/R$--$\Sigma$ relation at a given gas mass surface density $\Sigma$. 
The variation in $\sigma_{\rm gas}^2/R$ with $\Sigma$ seen here suggests that column density is not a fundamental properties of 
molecular clouds. Previous studies suggest that the observed mass-size relation of molecular clouds 
is solely a result of $\rho\propto M R^{-3}$ and may be an artifact of the limited range of 
column densities a specific molecular line tracer is sensitive to \citep[see e.g.,][]{Ballesteros02a, Ballesteros11a}.
%For instance, \citet{Ballesteros02a} show that the density
%of clouds ($\rho$) is independent of their size ($R$) when one properly extract these quantities in three-dimensional space instead of
%two-dimensional space; the latter is done in \obs.
%When they project the clouds into two-dimensional space and measure the densities and sizes of clouds for a given
%line tracer, they find $\rho \propto R^{-1}$, which is unsurprising since $N_H$ is just a constant.
%They therefore argue that the mass-size relation is simply a result of $\rho\propto M R^{-3}$
%observed in 2D-space at a fixed column density (cf. an actual physical relation of $M \propto R^{4/3}$ claimed in
%observational studies). % where $\rho$ would be proportional to $R^{-1/2}$
%% since $M$ would then scale as $R^{3}$ (ånd naturally display a linear relationship in $\log M - \log R$ plot).

@@

% Starburst
In the starburst phase, MCCs have velocity dispersion and sizes similar to those in the accreting phase; however, 
MCCs in the starburst phase span a wider range in gas surface density 
(bottom panels of \Fig{larsons_single}) and have lower virial parameters.
That is, MCCs in the starburst phase are more susceptible to collapse, as expected.
The gas surface density of MCCs in both accreting and starburst phases is higher than that in the solar neighborhood
of the Milky Way and the Large Magellanic Cloud (LMC), but comparable to those observed in starburst galaxies and the nearby 
ultra-luminous IR galaxies (ULIRGs) \citep{Boulares90a, Scoville91a, Weiss01a, Hughes10a, Leroy15a}.
% LMC: 0.01 g cm^-2
% M82: 0.1 g cm^-2
% Arp 220: 7-20 g cm^-2
%
% Due to a time delay between cloud collapse and \SF, we also compare the virial parameter of MCCs in the pre-starburst phase and post-starburst phase.
%\Fig{alphaEvol} shows that most MCCs in the pre-starburst phase have even lower virial parameter than in the starburst phase. On the other hand,
%the virial parameter of MCCs in the post-starburst phase is higher than in both the pre-starburst and the starburst phase.
%This is consistent with our physical intuition of gas instability leading to \SF.

@@

The sizes of MCCs are dependent on the choice of $n_{\rm cut}$ in the following ways.
As mentioned in \Sec{dist}, the most massive cloud identified at low H$_2$ gas density thresholds
corresponds to the molecular disk of \flower, which is broken down into multiple smaller MCCs at higher 
$n_{\rm cut}$\footnote{That said, there are fewer MCCs at highest $n_{\rm cut}$ than the lowest $n_{\rm cut}$ 
 since there are fewer cells in the simulations with correspondingly high H$_2$ gas densities.}.
Second, excluding such structure, some MCCs are further broken down into smaller MCCs at higher $n_{\rm cut}$ 
(see top panels of \Fig{alpha16-28}). 
At the resolution limit of our simulation, most MCCs studied in this work have $R\simeq$\,50\,pc (see also \Fig{dist}).
%
%For instance, the cluster of points found at the lowest density threshold, 
%occupying the top right corner of the linewidth-size relation in the top left panel of \Fig{alpha16-28}, 
%are broken down into smaller MCCs at the highest density threshold (see top right panel of the same figure\footnote{Note
%that while the biggest MCCs are broken into smaller MCCs at higher $n_{\rm cut}$, 
%MCCs identified at lower density in the outskirts of \flower
%typically do not reach the density thresholds as $n_{\rm cut}$ increases. Hence, there are fewer MCCs at the highest density threshold.}).
%%
%These MCCs are smaller in size, and thus, occupy the leftward in the top right panel.

@@

At the highest density cut, only the densest gas structures are identified.
The virial parameter of these MCCs are, on average, lower than those identified at low $n_{\rm cut}$, and are thus, more 
unstable against collapse (see middle right panel of \Fig{alpha16-28}).

@@

In this section, we compare the observable quantities of MCCs obtained from the simulations (e.g., $\sigma_{\rm gas}$, $R$, $M_{\rm gas}$, $\Sigma_{\rm gas}$) with those of molecular gas structures from \obs at lower redshift.
%%
%We exclude the biggest MCC identified in each evolutionary stage, which correspond to the main disk of \flower (i.e., the top right cluster of points in the linewidth-size relation of \Fig{larsons_single} and the top left panel of \Fig{alpha16-28}).
The velocity dispersion of MCCs in \flower is similar to those observed in $z$\ssim2 spatially resolved studies of gas-rich star-forming galaxies, 
spanning a range of $\sigma_{\rm gas}\simeq$\,20$-$80\,\kms (\Fig{larsons_single}; see e.g., \citealt{Swinbank11a}). 
However, the sizes of MCCs are almost a factor of two smaller. This likely suggest that the sizes of \highz molecular gas structures reported in the literature
are limited by the spatial resolution. 
%
The velocity dispersions of some MCCs are also comparable to the most turbulent gas clouds observed in the inner Milky way and nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a, Leroy15a}), which lies along the locus of $\sigma_{\rm gas}\propto R^{0.56}$. Such high velocity dispersion 
in \flower is dominated by non-thermal energy (\Fig{vv}) and results from the injection of kinetic energy from recent \SF as \flower is assembling its stellar mass (given the high Mach numbers of MCCs; \Sec{distribution}). In fact, by the accreting stage (see \Fig{SFH}a) at $z\simeq$\,7.2, \flower has assembled a stellar mass of $M_\star$\eq7.5\E{9}\,\Msun.

@@

% different evolutionary stages
We do not find any major quantitative differences in the MCCs of \flower between its accreting and starburst phase 
with respect to those observed in the nearby Universe (see \Fig{larsons_single}), which are separated by $\simeq$300\,Myr. However, MCCs in the \SB phase have lower $\alpha_{\rm vir}$ compared to the accreting phase. This is expected for \SF to proceed.

@@

Close resemblance of the $Q_{\rm eff}$ and $Q_{\star}$ maps indicates that contributions from the stellar component play an important role in governing the stability of the MCCs against perturbations. This can be understood since stars in \flower dominates the central part of the galaxy in mass, so their gravitational potential provides a non-negligible contribution to the instability. In fact, this is also illustrated by the differences seen between $\alpha_{\rm vir}$ and $\alpha_{\rm vir, tot}$ 
of the most massive structure (i.e., the gas disk of \flower; see \Fig{larsons_single}).
Similarly, contribution from the thickness of the disk is important in \flower since its disk is warped and has a scale height-to-radius ratio of $h/r_{\rm gal}$\ssim150\,pc/1\,kpc\,$\simeq$\,0.15.
% 
That is, some MCCs are found in regions of $Q_{\rm gas}$\ssim1, which is consistent with the expectation that they correspond to regions of high surface densities that are gravitationally unstable. Note, however, that when including the stabilizing effects due to the stellar potential of \flower and the thickness of its disk (via $\sigma_z$, i.e., $Q_{\rm eff}$; see Equation~\ref{eqn:q_eff}), some of these MCCs are consistent with $Q_{\rm eff} > 1$. 
%
This demonstrates the importance of accounting for stellar contribution and disk thickness when examining the stability of molecular gas structures. This consideration is especially relevant for the relatively evolved and enriched systems at high redshift, that are preferentially being imaged at high resolution with ALMA. In the outer regions of \flower, on the other hand, $Q_{\rm eff}$ resembles $Q_{\rm gas}$, with both $\log{Q_{\rm gas}}$ and $\log{Q_{\rm eff}} < -1$. Notably, these are the more gas-rich regions (see \Fig{sigma}).

The large ($>$\,2) virial parameters seen in some MCCs of \flower can be understood by first noting that fragmentation {\em can} happen in regions of low $Q$ (if we only consider instability against axisymmetric perturbations), but further evolution and gas collapse depends on the equation of state of the gas.
%
Such fragmentation is expected to take place at the critical scale length $\lambda_{\rm crit} < 2 \pi^2 G \Sigma / \kappa^2$. Second, this fragmentation scale is greater than the typical size of GMCs.
%
This could be interpreted as a result of instability setting the scales for fragmentation, {\em but the truly star-forming regions correspond to the collapsing, denser, and cooler molecular structures that are on smaller scales}.
%
Thus, the high virial parameter found for some MCCs in \flower indicates that they are not the collapsing structures and are found in regions of $Q_{\rm eff}>1$. On the other hand, MCCs in (the denser) regions with a lower Toomre $Q_{\rm eff}$ parameter are more unstable, and \SF may take place within its star-forming {\it clumps} and {\it cores} on smaller scales, where energy quickly dissipates.

If most of the MCCs in \flower are stable against collapse, how does it sustain its high SFR of $\sim$70\,\Msun\,yr\pmOne in the starburst phase? Such tension in the interpretation is understood as follows.
%
First, due to energy dissipation on small-scales, such MCCs are no longer supported by turbulence. This in turn would enable
sub-regions of the MCCs to collapse and potentially form OB associations out of these unbound MCCs \citep{Clark04a, Clark05a}.
% Mechanisms causing non-axisymmetric perturbations (e.g., arms) to the gravitational potential \MM{Gravitational instability is that mechanism (see e.g.\ Wada et al.'s classic review of the subject (2011, doi:10.1017/S1743921311000640), so this isn't really a separate mechanism.} can induce orbit crossing, shocks and dissipation in gas, promoting turbulence dissipation and collapse on smaller scales to trigger \SF. These mechanisms are likely important given high $Q_{\rm eff}$ found across \flower and its few tens of solar masses per year SFR, albeit sporadic.
Further, the SFR of \flower is very bursty and high SFR stages are only transient.
%
Finally, our results are limited by the resolution of the simulation, i.e., in \flower~we do not resolve \SF in {\it cores} and {\it clumps} as in the classical molecular cloud hierarchy. This re-iterates the statement about low $Q$ above.

% \AP{I think we should add a in-text comparison with the following \citet{grisdale:2017,grisdale:2018,grisdale:2019}, particularly the \citet{grisdale:2017}, similarly to what we have done for \citet{Behrendt16a}}

@@

The sizes of MCCs are only somewhat dependent on the choice of $n_{\rm cut}$, after excluding the 
most massive molecular structure identified (which correspond to the main disk of \flower). 
The main disk is break into multiple MCCs at higher $n_{\rm cut}$. The $\sim$200\,pc-scale MCCs found with a low density threshold correspond to the arms of the disk of \flower and break down into smaller $\lesssim$100\,pc-scale MCCs at higher density thresholds.
%
Excluding the biggest MCC, the typical mass of MCCs is $10^{6.5}$\,\Msun. Similarly massive molecular structures have been observed in nearby star-forming and starburst galaxies \citep[e.g.,][]{Keto05a, DonovanMeyer13a, Colombo14a, Leroy15a}, and reported in idealized (no stellar feedback) isolated (no cosmological initial conditions) galaxy simulations done at higher resolution (e.g., $l_{\rm cell}\simeq3$\,pc in the 48\,kpc box studied by \citealt{Behrendt16a}). That said, the similar mass range found in MCCs of \flower\ is reassuring --- our results are not far off despite the resolution limit ($l_{\rm cell}\simeq$\,30\,pc). On the other hand, the gas velocity dispersion $\sigma_{\rm gas}$ is rather insensitive to the adopted density threshold.
